### 2019-02-22 sections/introduction.tex
moved first part of 1.1 to intro

\fixme{Common intro??}

@@

In this paper, we want to take a step back and look at the essence of \TOP.
We do this both formally and informally.
Informally in the sense that we give an intuitive description of the features that define task-oriented programming.
Formally in the sense that we develop a calculus which formalizes these features as language constructs, and we give them semantics in the style that is common in programming language research.

>>>>

@@

In this paper, we want to take a step back and look at the essence of \TOP.
We do this both formally and informally.
Informally in the sense that we give an intuitive description of the features that define task-oriented programming.
Formally in the sense that we develop a calculus which formalises these features as language constructs, and we give them semantics in the style that is common in programming language research.
